---
title: "Lab 00 - Hello IDS!"
author: "Omar"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("joel", " ben", "lilia", 
           "jamie", "omar"),
  github_username = c("baron/joe", " benstenton", "omarmwahdan", 
                      "leilahookway", "jamiekerr06"), 
  colour = c("forestgreen", "red", "maroon", 
             "blue", "lightblue"),
  hobby = c("rugby", "football", "guitar", 
            "badminton", "football"),
  favourite_number = c(2, 6, 9, 9, 10)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


plot shows our username by the x axis and by the y axis our favourite number and its a bar graph not in order of ascending numbers as everyone has different favourite nunbers!
### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "colour", 
          y = "numbers",
          title = "numbers against colours")
```


### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

Classifying the groups like musical instruments being together, opendoor sports together, etc. You can see how many people do a sport in a more organised way. You can also see who does sports as a total count. 
